
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small {
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/rdwatkin}{\Large Ryan Watkins}} & Email : \href{mailto:rdwatkin@outlook.com}{rdwatkin@outlook.com}\\
  \href{https://github.com/rdwatkin}{https://github.com/rdwatkin} & Mobile : +1-858-880-5959 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Santa Cruz}{Santa Cruz, CA}
      {Bachelor of Science in Computer Science, Minor in Economics;  GPA: 3.52}{Sep. 2016 -- Jun. 2020}
    \resumeSubheading
      {La Jolla Country Day School}{San Diego, CA}
      {High School Diploma;  GPA: 3.94 }{Sep. 2012 -- May. 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
  \resumeSubheading
      {Software Intern}{Jul. 2018 - Sep. 2018}
      {Gemini Design}{Poway, CA}
      \resumeItemListStart
        \resumeItem{User Interface Design}
          {Designed and implemented a serial communication port monitor using Microsoft Visual Studio C\# which could send commands and receive data from USB. }
        \resumeItem{Embedded Systems}
          {Developed firmware in C for a Nucleo F401re to communicate with the company's custom board over SPI and to send and receive data through a computer's serial communication port using USART thereby enabling the company to control their custom board from a GUI. }
        \resumeItem{Scholarship}
          {Selected to receive the Gemini Design Engineering Scholarship at the end of the summer internship for my abilities to quickly come up to speed on new technologies. }
      \resumeItemListEnd
  
    \resumeSubheading
      {IT Intern}{Jul. 2017 - Sep. 2017}
      {Patenaude and Felix APC}{San Diego, CA}
      \resumeItemListStart
        \resumeItem{Cloud Work Environments}
          {Conducted researched on and assisted an office-wide shift from local machines to cloud-based desktops which saved the company money by replacing costly thick clients with more cost-effective thin clients.}
        \resumeItem{Electronic Data Interchange}
          {Maintained and updated electronic client data daily to ensure the company information was always up to date. }
        \resumeItem{Help Desk}
          {Promptly handled repair requests on a broad range of office technologies to maximize work space efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {File Clerk}{Jun. 2017 - Sep. 2017}
      {The Watkins Firm}{San Diego, CA}
      \resumeItemListStart
        \resumeItem{Billing}
          {Routinely updated the company's client billing logs to ensure company files were always current.}
        \resumeItem{Documentation}
          {Maintained appropriate physical and electronic filing of  professional legal documents.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Client-Server File Transfer System}
      {Secure file transfer system which properly handles fork requests, race conditions, and interactive commands in C++.}
    \resumeSubItem{Web Browser}
      {Single Pane lightweight web browser with GUI interface created with JavaFX.}
    \resumeSubItem{Graphics Library}
      {Graphics library for display, selection, and alteration of commonly used OpenGL designs in C++.}
    \resumeSubItem{Simulated File Tree}
      {Shell designed in C++ to navigate a simulated file tree hierarchy.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Java, C++, C, C\#, SQL, \LaTeX}
      \hfill
      \textbf{Technologies}{: OSX, Windows, Unix/Linux}
    }
  \resumeSubHeadingListEnd


%-------Leadership and Volunteer Experience--
\section{Extracurriculars}
    \resumeSubHeadingListStart
        \resumeSubItem{Computer Technician Club}{Founder of the computer technicians club which taught its members the content required to pass the 220-801 CompTIA A+ Exam.}
        \resumeSubItem{Cyber Patriots}{Leading member of the LJCDS cyber security team which routinely competed in image security tournaments.}
        \resumeSubItem{Volunteer Work}{Frequently participate in local volunteer work with organizations such as The Santa Cruz Boys \& Girls Club, Gault Elementry School, Capitola beach clean-up, etc.}
        \resumeSubItem{Intramurals}{Basketball and Volleyball}
    \resumeSubHeadingListEnd


%-------------------------------------------



\end{document}

